---
title: "Victor Murra Schott"
---

## Welcome!

Hi, I'm Victor Murra Schott, a student at Baruch College. This site documents my coursework and projects for the semester.

### About Me
I'm currently studying business analytics with a focus in marketing analytics, and working at DIRECTV as a systems analyst. Outside of school and work I like to spend my time outdoors playing golf and softball, as well as playing the piano.

### Links
- [My Resume](Victor Murra Schott Resume 2026.pdf)
- [Github Profle](https://github.com/victorms-4)
- [LinkedIn](https://www.linkedin.com/in/victor-murra-schott/)

### Contact
You can rech me at [victor.murraschott@gmail.com]

```{r}
#| echo: false
#| message: false
#| warning: false

if(!require("leaflet")){
    options(repos=c(CRAN="https://cloud.r-project.org"))
    install.packages("leaflet")
    stopifnot(require("leaflet"))
}

baruch_longitude <- -73.98333
baruch_latitude  <- +40.74028

leaflet() |>
  addTiles() |>
  setView(baruch_longitude, baruch_latitude, zoom=17) |>
  addPopups(baruch_longitude, baruch_latitude, 
            "I am a Master's student at <b>Baruch College</b>!")
```
```{r}
#| include: false
1+1
```
--------------
Last Updated: `r format(Sys.time(), "%A %m %d, %Y at %H:%M%p")`